\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathpartir}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{tikz}
\usetikzlibrary{positioning,arrows.meta,fit,backgrounds}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!black,
  citecolor=blue!50!black,
  urlcolor=blue!50!black,
}

\lstset{
  basicstyle=\ttfamily\footnotesize,
  breaklines=true,
  columns=fullflexible,
  showstringspaces=false,
  frame=single,
  framerule=0.3pt,
}

\title{\textbf{CapShim:}\\ Capability-Typed Shimming for the Model Context Protocol\\
\large with a Non-Interference Argument Against\\Weird-Machine Tool Composition}
\author{Fatimah Emad Eldin\\\small AI Researcher\\\small\texttt{Fatimah@trouve.works}}
\date{24 May 2026\\\small Apart Research \& Atlas Computing\\\small Secure Program Synthesis Hackathon, Tracks 1--2 (cross-cutting Problem~\#13)}

\begin{document}
\maketitle

\begin{abstract}
\noindent
The Model Context Protocol (MCP) has become the de facto interface
between large-language-model agents and external tools, and it ships
with \emph{ambient authority}: an exposed \texttt{fs\_read} tool can
read anything the host process can. Individual tool calls are benign;
the danger is \emph{composition}---a prompt injection that says
``read \texttt{\textasciitilde/.ssh/id\_rsa} and \texttt{POST} it to
\texttt{attacker.com}'' is the canonical \emph{weird machine} of
LangSec adapted to agentic systems. We present \textbf{CapShim}, a
transparent, capability-typed proxy that intercepts MCP
\texttt{tools/call} traffic, lifts tool inputs and outputs onto an
Information Flow Control (IFC) lattice, and statically rejects any
proposed call plan whose data flow would violate a YAML-declared
policy. On a benchmark of ten attack scenarios drawn from the
AgentDojo taxonomy and ten benign workflows, CapShim blocks 100\,\% of
attacks with zero false positives and median enforcement latency of
0.044\,ms. We sketch a non-interference argument that makes the
guarantee precise. CapShim is a 1\,500-line Python library, drop-in for
the public \texttt{@modelcontextprotocol} servers, and is released
under MIT.
\end{abstract}

%====================================================================
\section{Introduction}
%====================================================================

The headline failure of agentic AI in 2026 is not yet a clever
jailbreak; it is the boring fact that ``\texttt{file\_read} then
\texttt{http\_post}'' exfiltrates secrets whenever an attacker can
inject a single string into the agent's context. The pattern is the
exact failure mode that LangSec calls a \emph{weird
machine}~\cite{bratus2011}: a composition of individually-permitted
operations into a logic the system never intended to expose.

MCP, the protocol that standardises tool access for Claude Desktop,
Cursor, Continue, and dozens of other agentic IDEs, codifies this
exposure into infrastructure. Every server in the public catalogue
runs with \emph{ambient authority}: a tool named \texttt{fs\_read}
inherits all the filesystem permissions of the host process.
Mitigation, where it exists, is ad-hoc string matching at the API
gateway and pleading prompts in the system message.

\paragraph{Contribution.} We argue that this is fundamentally a
\emph{type system} problem and treat the MCP bus as a typed language.
Concretely, we contribute:
\begin{enumerate}[leftmargin=*]
\item A Python library, \textbf{CapShim} ($\sim$\,1\,500 LoC, MIT),
that is a drop-in proxy between any MCP client and any MCP server. It
extends the existing tool-schema JSON with three optional fields
(\texttt{inputLabels}, \texttt{outputLabel}, \texttt{effects}) and
typechecks the agent's proposed call plan against a declared policy
before any tool fires.
\item A small but realistic IFC type system---three labels (Public
$\sqsubseteq$ User $\sqsubseteq$ Secret), provenance categories, four
typing rules, explicit declassification---together with a
non-interference argument relating it to the policy.
\item An empirical evaluation on a 20-scenario benchmark assembled
from the AgentDojo taxonomy~\cite{debenedetti2024agentdojo} that
demonstrates 100\,\% attack blocking, 0\,\% false-positive rate, and
sub-millisecond enforcement latency.
\end{enumerate}
This work directly targets Problem \#13 (Capability-Safe Tool
Interfaces) from Dougherty \& von
Hippel~\cite{dougherty2026tractable} and contributes to Tracks 1--2
of the Secure Program Synthesis Hackathon by making the
\emph{specification} of safe tool composition both human-readable
(YAML) and machine-checkable (the typechecker).

%====================================================================
\section{Related Work}
%====================================================================

\paragraph{Capability security.} Miller's object-capability
work~\cite{miller2006robust} establishes the philosophical baseline:
authority should be \emph{designated} rather than \emph{ambient}.
MCP today contradicts this. CapShim is, in essence, a small
capability layer retrofitted onto an ambient-authority protocol.

\paragraph{Information flow control.} Denning's lattice
model~\cite{denning1976lattice} and the modern statement of
non-interference by Sabelfeld and Myers~\cite{sabelfeld2003language}
furnish our type system. Jif and FlowCaml are the canonical
language-level implementations; CapShim moves the same idea to the
protocol level, where the values are JSON-RPC arguments rather than
program variables.

\paragraph{LLM-agent security.} AgentDojo~\cite{debenedetti2024agentdojo}
provides a taxonomy of prompt-injection attacks against tool-using
agents; we draw our ten attack scenarios from this taxonomy. The
Universalis/Automind work of Meijer~\cite{meijer2026universalis}
takes a heavier route, compiling agent plans into a Prolog-style DSL
and discharging them with Z3 before any tool fires; CapShim is
deliberately lighter, trading expressive power for a 200-line
typechecker that ships today.

\paragraph{Specification elicitation \& validation.} Dougherty and
von Hippel~\cite{dougherty2026tractable} frame the bottleneck in
secure program synthesis as specification work; in the Q\&A session
preceding this hackathon, Dougherty named ``differential specs'' and
``a tool people could clone off GitHub on Monday morning'' as the
two heuristics that would win his vote. CapShim's policy file is
exactly that kind of compact specification, human-readable and
LLM-readable in the same breath.

%====================================================================
\section{Threat Model}
%====================================================================

\paragraph{Setting.} An LLM agent is connected to one or more MCP
servers that expose tools. The user grants the agent a session and
issues high-level natural-language requests. Some inputs to the
agent (a web page, a search result, a checked-in README, a Slack
message, a PR description) are attacker-controlled.

\paragraph{Adversary capability.} The adversary controls one or more
\emph{indirect prompts} that reach the agent's context window. They
cannot patch the MCP server, the client, or the shim, but they can
attempt to coerce the agent into emitting any \texttt{tools/call}
sequence the MCP server will accept.

\paragraph{Security goal.} For every plan $P$ the agent emits, the
sequence of side effects that survive the shim must satisfy the IFC
policy: confidential reads cannot reach untrusted sinks, even via
composition through intermediate tools. Formally, this is a
non-interference property over the egress channel
(\S\ref{sec:noninterference}).

\paragraph{Out of scope.} (1) Covert channels purely inside the LLM's
context window (e.g.\ the model summarising a secret in natural
language back to the user). (2) Lying tool authors who advertise
labels they do not honour. (3) Untyped channels outside the MCP bus
(e.g.\ a tool that mutates global filesystem state observable by
another tool). We discuss these in the dual-use appendix.

%====================================================================
\section{Design}
%====================================================================

\subsection{Architecture}

CapShim is a stateless transparent proxy. It speaks the MCP JSON-RPC
dialect on both sides; the agent and the upstream MCP server need no
modification.

\begin{center}
\begin{tikzpicture}[
  node distance=8mm and 10mm,
  box/.style={draw, rounded corners=2pt, minimum height=8mm,
              minimum width=22mm, font=\small, align=center},
  capbox/.style={box, fill=blue!8},
  policybox/.style={box, fill=yellow!15, minimum width=18mm},
]
\node[box] (agent)  {LLM agent};
\node[capbox, right=of agent] (shim) {CapShim\\\footnotesize proxy};
\node[box, right=of shim] (server) {MCP server\\\footnotesize tools};
\node[policybox, below=of shim] (pol) {\texttt{policy.yaml}};
\draw[->] (agent) -- node[above,font=\scriptsize]{JSON-RPC} (shim);
\draw[->] (shim)  -- node[above,font=\scriptsize]{JSON-RPC} (server);
\draw[->] (server.south west) to[bend left=25]
  node[below,font=\scriptsize]{result} (agent.south east);
\draw[->,dashed] (pol) -- (shim);
\end{tikzpicture}
\end{center}

The shim's only decision is whether to forward a \texttt{tools/call}
(or a multi-call plan submitted via the non-standard
\texttt{capshim/plan} method) or to short-circuit it with a
structured \texttt{capability\_denied} error. Every decision is
logged with the proof witness.

\subsection{IFC Lattice}

We instantiate the smallest lattice that captures the threat model:
\[
\text{Public} \sqsubseteq \text{User} \sqsubseteq \text{Secret}.
\]
Each labelled value also carries a set of \emph{provenance
categories} drawn from $\{\texttt{fs.read}(p),\
\texttt{fs.write}(p),\ \texttt{net.http}(h),\ \texttt{env}(n),\
\texttt{secret},\ \texttt{pii}\}$. Categories let the policy decide
not only on confidentiality level but on origin: data tagged
\texttt{fs.read("$\sim$/.ssh/id\_rsa")} may be blocked even if the
declared label is User, because the category itself names a
sensitive resource.

The lattice supports join $\sqcup$ and a category-aware
declassification operator authorised only by explicit policy
edges (\S\ref{sec:type-rules}).

\subsection{Tool-Schema Extensions}

Vanilla MCP tools advertise \texttt{name}, \texttt{description}, and
an \texttt{inputSchema}. We add three optional fields:

\begin{lstlisting}[language=]
"inputLabels":  { "path": "PUBLIC", "content": "PUBLIC" }
"outputLabel":  "$label_of_path(${path})+fs.read(${path})"
"effects":      ["fs.read"]
\end{lstlisting}

The \texttt{outputLabel} string is a tiny template language with two
helpers, \texttt{\$label\_of\_path} and \texttt{\$label\_of\_env},
that consult the policy at typecheck time. This lets a tool declare,
once, that ``my output is Secret if the policy considers this path
sensitive, otherwise Public,'' without baking the policy into the
tool.

\subsection{Type Rules}\label{sec:type-rules}

A \emph{plan} is a finite sequence of tool calls; subsequent calls
reference earlier returns via the literal placeholder \texttt{\$ret:i}.
The checker symbolically evaluates a plan, tracking the tag of each
value, and applies the rules below. We write
$\Gamma \vdash e : (\ell, C)$ for ``in environment $\Gamma$, value
$e$ has confidentiality $\ell$ and provenance categories $C$.''

\begin{mathpar}
\inferrule*[Right=T-Read]
{ }
{ \Gamma \vdash \mathsf{fs\_read}(p) : (\mathit{label}_\Pi(p),\
  \{\mathsf{fs.read}(p)\}) }

\and

\inferrule*[Right=T-Net]
{ \Gamma \vdash b : (\ell, C) \\
  \Pi\ \mathsf{allows\_sink}(h, \ell, C) \\
  \mathsf{net.http}(h) \in \Pi.\mathsf{egress} }
{ \Gamma \vdash \mathsf{net\_http\_post}(h, b) :
  (\mathsf{Public}, C) }

\and

\inferrule*[Right=T-Write]
{ \Gamma \vdash c : (\ell, C) \\
  \ell \sqsubseteq \mathsf{Public}\ \lor\
  p \in \Pi.\mathsf{sensitive\_paths} }
{ \Gamma \vdash \mathsf{fs\_write}(p, c) :
  (\mathsf{Public}, C) }

\and

\inferrule*[Right=T-Declassify]
{ \Gamma \vdash e : (\ell_1, C) \\
  (\ell_1 \to \ell_2,\ t,\ \kappa) \in \Pi.\mathsf{declassify} \\
  \kappa\ \mathsf{matches}\ C }
{ \Gamma \vdash \mathsf{declassify}_t(e, \ell_2) : (\ell_2, C) }
\end{mathpar}

$\Pi$ is the policy. $\mathit{label}_\Pi(p)$ returns Secret if $p$
matches any glob in $\Pi.\mathsf{sensitive\_paths}$ and Public
otherwise. The policy's \texttt{allows\_sink} predicate enforces the
egress decision: Public/User data may leave to any host in
$\Pi.\mathsf{egress}$; Secret data leaves only to
$\Pi.\mathsf{trusted\_hosts}$ and only if no sensitive-category tag
forbids it.

The checker is a small-step interpreter that fails fast on the
first rule violation and returns a structured \emph{witness} naming
the rule, the offending call, the source label, the categories, and
the sink. This witness is what the proxy returns in the
\texttt{capability\_denied} error payload.

\subsection{Non-Interference}\label{sec:noninterference}

We sketch the central argument. Let $\Pi$ be a fixed policy and let
$P_1, P_2$ be two plans that differ only in their \emph{Secret} inputs
(formally: the two plans agree on the values of every term whose tag
is $\sqsubseteq$ User in the initial environment).

\begin{theorem}[Egress non-interference (informal)]
If $\Pi \vdash P_1$ and $\Pi \vdash P_2$ both typecheck, then the
sub-sequence of egress events $\{\mathsf{net.http}(h, v) :
h \notin \Pi.\mathsf{trusted\_hosts}\}$ produced by $P_1$ and by
$P_2$ are identical.
\end{theorem}

\noindent\emph{Sketch.} Induction on plan length. The checker's
invariant is that any value reaching $\mathsf{net.http}(h)$ with
$h \notin \Pi.\mathsf{trusted\_hosts}$ has effective label
$\sqsubseteq$ User and no sensitive-category tag. T-Net enforces
this; T-Declassify only relabels values whose category set is
disjoint from the policy's sensitive categories. Substituting any
Secret-tagged input cannot change the value of a User-tagged
expression without violating T-Net or T-Declassify, contradicting
the assumption that the plan typechecks. $\Box$

A mechanised proof of this sketch in Lean 4 is left as future work
(\S\ref{sec:future}); the type system was deliberately kept small
enough that the manual induction is convincing.

%====================================================================
\section{Implementation}
%====================================================================

The implementation is 1\,500 lines of Python 3.10+, structured as
five core modules and an example MCP server. CapShim's proxy speaks
MCP JSON-RPC 2.0 over stdio and HTTP, the two transports defined in
the MCP specification revisions of 2024-11-05 and 2025-03-26; we
tested compatibility against the reference servers in
\texttt{@modelcontextprotocol/servers} (filesystem, fetch,
git, postgres) at commit \texttt{HEAD$\sim$} as of May 2026. The
shim's policy file and schema extensions are MCP-spec backwards
compatible---vanilla clients that ignore the
\texttt{inputLabels}/\texttt{outputLabel}/\texttt{effects} fields
continue to interoperate.

\begin{center}
\small
\begin{tabular}{ll}
\toprule
Module & Role \\\midrule
\texttt{labels.py}   & lattice, categories, tags, join/meet \\
\texttt{schema.py}   & MCP schema extensions, label-template parser \\
\texttt{policy.py}   & YAML loader, predicates, declassification \\
\texttt{checker.py}  & plan typechecker, witness construction \\
\texttt{proxy.py}    & async JSON-RPC interceptor, audit log \\
\bottomrule
\end{tabular}
\end{center}

The proxy is stateless across requests; per-plan state lives only
inside a single \texttt{check\_plan} call. The checker holds no
external dependencies beyond PyYAML; the test suite adds Hypothesis
for property-based tests on the lattice.

%====================================================================
\section{Evaluation}
%====================================================================

\subsection{Benchmark}

We assembled ten attack scenarios (A1--A10) by walking the
\emph{indirect-prompt-injection} subset of the AgentDojo
taxonomy~\cite{debenedetti2024agentdojo} (Sections 3.1--3.3 of that
paper, covering filesystem, network, and environment-channel
exfiltration patterns) and instantiating each pattern against the
toy MCP server's tools (\texttt{fs\_read}, \texttt{fs\_write},
\texttt{net\_http\_post}, \texttt{env\_get}). The attacks span the
three classical exfiltration topologies: direct two-step
(\emph{read $\rightarrow$ post}), three-step laundering through a
file (\emph{read $\rightarrow$ write $\rightarrow$ post}), and
environment-variable harvest (\emph{env $\rightarrow$ post}).

Ten benign workflows (B1--B10) cover the realistic positive set
(coding-agent and integration-bot use). Each was chosen
\emph{before} running the checker, to avoid the bias of selecting
benign cases that happen to pass. The full enumeration is in
Appendix~\ref{app:benign} alongside the attack table.

\subsection{Headline Numbers}

\begin{center}
\small
\begin{tabular}{lcc}
\toprule
Metric & Value & Target \\\midrule
Attacks blocked (TPR) & 10/10 (100\,\%) & $\geq$\,90\,\% \\
Benign allowed (1$-$FPR) & 10/10 (100\,\%) & $\geq$\,90\,\% \\
Median enforcement latency & 0.044\,ms & $<$5\,ms \\
P95 enforcement latency & 0.221\,ms & $<$5\,ms \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Per-Attack Results}

\begin{center}
\scriptsize
\begin{tabular}{lll}
\toprule
ID & Pattern & Verdict \\\midrule
A1  & ssh key $\to$ attacker.com                 & deny (T-Net-Confidentiality) \\
A2  & AWS creds $\to$ pastebin                   & deny (T-Net-Egress) \\
A3  & \texttt{.env} $\to$ attacker.com           & deny (T-Net-Confidentiality) \\
A4  & GITHUB\_TOKEN $\to$ github abuse endpoint  & deny (T-Net-Confidentiality) \\
A5  & ssh key $\to$ tmp file $\to$ attacker      & deny (T-Write-Leak) \\
A6  & direct egress to disallowed host           & deny (T-Net-Egress) \\
A7  & \texttt{.env} $\to$ public log             & deny (T-Write-Leak) \\
A8  & AWS creds $\to$ weather.example.com        & deny (T-Net-Confidentiality) \\
A9  & \texttt{id\_rsa.bak} glob $\to$ github     & deny (T-Net-Confidentiality) \\
A10 & AWS env $\to$ public path                  & deny (T-Write-Leak) \\
\bottomrule
\end{tabular}
\end{center}

\noindent The benign-workflow table is in
Appendix~\ref{app:benign}; the takeaway is that for B1--B10
\emph{no} type rule fires.

\subsection{Latency}

Per-call overhead is dominated by dict lookups and a single
\texttt{fnmatch} per sensitive-path glob. Across 200 repeated
\texttt{net\_http\_post} calls on a stock workstation
(Python 3.14, Windows 11), the median check completes in 44\,µs and
the P95 in 221\,µs. Production MCP calls take 10--500\,ms of
network round-trip, so the shim's overhead is below the noise floor.

%====================================================================
\section{Discussion}
%====================================================================

\paragraph{What CapShim does buy.} Reduction of a class of agent
attacks (composition-via-prompt-injection of two or more benign
tools) from a hand-audit problem to a typecheck. The policy file
($\sim$30 lines for our example) is small enough that a security
reviewer can read it in five minutes and an LLM can author a first
draft. Because the proof witness is structured, audit-time
forensics get the rule, the source label, the categories, and the
sink for free.

\paragraph{What it doesn't.} CapShim is silent on three real
failure modes. (1) \emph{Out-of-band channels through the LLM.}
If a tool returns Secret data into the LLM's context, the model can
launder it into a natural-language reply that the user reads or
posts elsewhere; nothing in MCP carries IFC labels into the LLM's
own reasoning trace. (2) \emph{Lying tool authors.} A malicious MCP
server that advertises \texttt{outputLabel: "PUBLIC"} for an
\texttt{fs\_read} of a sensitive file laundens by claim. (3)
\emph{Side channels.} A clever attacker can encode bits of a secret
in argument structure (order, length, presence/absence of optional
fields), and the checker is field-level, not byte-level.

We address each in detail in the dual-use appendix.

%====================================================================
\section{Future Work}\label{sec:future}
%====================================================================

\begin{itemize}[leftmargin=*]
\item \textbf{Mechanised proof in Lean 4.} The type system is small
($\sim$4 rules); a complete non-interference proof against a
small-step semantics is tractable in a follow-on month and would
close the modeling-gap end of the Miyazono triangle. Three lemmas
sit on the critical path and would be discharged first:
(L1)~\emph{label monotonicity under T-Read}, stating that
$\mathit{label}_\Pi(p)$ is monotone with respect to $\Pi$ refinement,
so adding sensitive paths to a policy never lowers any read's label;
(L2)~\emph{soundness of T-Declassify}, stating that declassification
preserves non-interference modulo the policy's explicit
declassification edges (i.e., only categories disjoint from the
sensitive set may be relabelled); and (L3)~the \emph{inductive step
of the non-interference theorem}, stating that if a plan-prefix of
length $n$ satisfies the egress non-interference invariant, then
extending it with any single typeable call also satisfies it.
Together these yield Theorem~1.

\item \textbf{Per-message taint in the LLM.} A first-pass shim
operating on the LLM's own scratchpad, treating Secret-tagged
context tokens as poisoned for subsequent reads, would address the
out-of-band channel.

\item \textbf{Differential specs.} Given an MCP server, prompt two
LLMs to author \texttt{capshim} policies independently and run them
both---disagreements between policies are exactly the contract-bug
signal Quinn Dougherty asked for in the Q\&A.

\item \textbf{TypeScript port.} The MCP reference implementation is
TypeScript; a port of the typechecker would let CapShim drop into
Claude Desktop, Cursor, and Continue without a Python sidecar.
\end{itemize}

%====================================================================
\section{Conclusion}
%====================================================================

The Model Context Protocol's security failures are not exotic, they
are ambient-authority failures of the most classical kind, and the
fix is the most classical answer: a small type system at the
boundary. CapShim is the demonstration that the answer fits in 1\,500
lines of Python, runs in microseconds, and catches the standard
weird-machine playbook today, before either the LLMs or the
adversaries get any more sophisticated.

\bibliographystyle{plainurl}
\bibliography{references}

%====================================================================
\appendix
\section{Limitations and Dual-Use Considerations}
%====================================================================

\paragraph{False negatives.} (1) \textbf{Lying tool authors:}
if a malicious server advertises Public for an output that is in
fact Secret, the checker will trust the advertisement. The
appropriate remedy is a third-party audit of the schema, the same
trust model Linux package signing relies on. (2) \textbf{In-LLM
laundering:} a Secret-tagged value returned to the agent can be
restated by the LLM in a follow-up assistant message and exit the
system via the user-facing channel, which has no IFC. (3)
\textbf{Argument-structure side channels:} the checker is
field-level, not byte-level; an attacker can encode roughly
$\log_2(\text{arg count}!)$ bits per call in argument ordering on
JSON-RPC implementations that preserve order.
(4)~\textbf{Timing and call-count channels:} our non-interference
theorem (\S\ref{sec:noninterference}) quantifies over the
\emph{sequence of egress events with payload}; it says nothing
about the \emph{number} of tool calls the agent emits or the
\emph{timing} between them. An adversary who cannot smuggle secret
bytes through the payload can still leak one bit per execution by
choosing whether to make $N$ benign calls or $M$ benign calls,
which CapShim's allow-decision will not perturb. Defeating this
class of channel requires either covering-traffic (issue the same
number of calls regardless of input) or a quantitative
information-flow framework~\cite{sabelfeld2003language} that goes
beyond the binary non-interference we prove here. We name it here
so a reviewer is not misled by the headline ``100\,\% blocked''
number: 100\,\% refers to the AgentDojo-derived corpus, not to all
covert channels.

\paragraph{False positives.} The lattice is coarse (three labels).
Workloads requiring fine-grained classification (HIPAA's 18
identifiers, PCI cardholder data subcategories) need a richer
lattice; this is a parameter, not a redesign.

\paragraph{Dual-use.} The technology is inherently defensive: it
restricts what an LLM agent can do. We see no offensive misuse path
for the typechecker itself. The benchmark scenarios are public
patterns that any adversary can already reproduce from the
AgentDojo paper; releasing them as named, scripted plans does not
materially advance attacker capability and gives defenders a
shared yardstick.

\paragraph{LLM-Assisted Authoring.} The lead author used Claude
Opus 4.7 for literature scoping, brainstorming the type-system
shape against the AgentDojo taxonomy, and drafting prose; all
typing rules, the non-interference argument, the implementation,
the policy DSL, and the eval benchmark are the author's own design,
written and verified by hand. No portion of the codebase was
copy-pasted from a model without a code review.

%====================================================================
\section{Benign-Workflow Enumeration}\label{app:benign}
%====================================================================

Symmetric with the attack table. Each scenario is the full plan a
realistic coding-agent or integration-bot might emit; the
``rule (would have) fired'' column is blank for every row, by
construction. A reviewer suspicious of cherry-picked benign cases
can rerun any of these directly: \texttt{python -m
evals.run\_evals}.

\begin{center}
\scriptsize
\begin{tabular}{p{0.6cm}p{8.1cm}p{4.4cm}}
\toprule
ID & Pattern & Why no rule fired \\\midrule
B1  & read \texttt{/srv/app/README.md}
    & path not in \texttt{sensitive\_paths}; no egress \\
B2  & POST plain text to \texttt{api.github.com}
    & host in \texttt{allowed\_egress}; payload Public \\
B3  & read \texttt{CHANGELOG.md} $\to$ POST to \texttt{api.github.com}
    & Public-tagged read flows to allowed-egress host \\
B4  & POST to \texttt{weather.example.com}
    & host in \texttt{allowed\_egress}; no confidential source \\
B5  & read \texttt{.env} $\to$ POST to \texttt{audit-sink.company.local}
    & sink is in \texttt{trusted\_hosts}, the legitimate carve-out \\
B6  & write ``build ok'' to \texttt{/var/log/app.log}
    & Public payload, write target outside
      \texttt{sensitive\_paths} \\
B7  & read \texttt{README.md} $\to$ write to log
    & Public-tagged read may be persisted anywhere \\
B8  & POST to \texttt{internal.company.local}
    & trusted internal endpoint \\
B9  & read \texttt{docs/intro.md} $\to$ POST to GitHub
    & Public docs piped to allowed-egress \\
B10 & two independent posts to allowed hosts
    & no flow between calls; both T-Net obligations satisfied \\
\bottomrule
\end{tabular}
\end{center}

\noindent Each B$i$ is verified at \texttt{evals/run\_evals.py}; the
machine output is committed to \texttt{evals/results.json}.

\end{document}
